
\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\bfseries\Large}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

\begin{center}
    {\LARGE \textbf{Vinod Kumar G}} \\
    \href{mailto:vinodkumar1947@gmail.com}{vinodkumar1947@gmail.com} \quad
    +1 (847) 456-9060 \quad
    \href{https://www.linkedin.com/in/vinod-kumar-gorrepati}{linkedin.com/in/vinod-kumar-gorrepati} \\
    \vspace{0.2cm}
\end{center}

\section*{Summary}
Senior Embedded Software Engineer with 13+ years of experience in designing, developing, and testing embedded and IoT systems. Proficient in Embedded C/C++, Python, real-time microcontroller programming (8/16/32-bit), IoT protocols (BLE, ZigBee, GSM, NB-IoT), and post-silicon validation. Demonstrated expertise in board bring-up, RTOS-based development, and secure, scalable firmware solutions across industries including automotive, HVAC, healthcare, and smart lighting.

\section*{Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} C, Embedded C, Python, Assembly
  \item \textbf{RTOS:} FreeRTOS, ThreadX, Contiki, OpenWRT
  \item \textbf{Protocols:} UART, SPI, I2C, MODBUS, CAN, BLE (4.0–5.2), ZigBee, GSM, NB-IoT, NFC, GPS
  \item \textbf{Tools/IDEs:} IAR, Keil, CCS, MPLAB X, AVR Studio, Lauterbach, Segger, Git, Jenkins
  \item \textbf{Microcontrollers:} STM32, MSP430, SAMD/SAML, nRF52, LPC2148, ATmega, BG96
  \item \textbf{Hardware:} Oscilloscope, Logic Analyzer, Eagle, KiCad, Altium, PCB design & bring-up
  \item \textbf{DevOps:} GitHub, GitLab, Jenkins, Jira, Confluence
\end{itemize}

\section*{Experience}

\subsection*{Senior Software Engineer – Susash Consulting (Client: Caterpillar Inc) — Sep 2022 to Oct 2023}
\begin{itemize}[leftmargin=*]
  \item Developed and integrated machine software libraries for embedded systems.
  \item Built configuration data sets and validated feature integration across subsystems.
  \item Managed software validation plans and coordinated defect resolution across teams.
\end{itemize}

\subsection*{Lead-II Embedded Software – UST Global — Mar 2021 to Jul 2022}
\begin{itemize}[leftmargin=*]
  \item Designed firmware for smart lighting controllers using NB-IoT and ZigBee.
  \item Led team in migrating legacy products and evaluating new technology platforms.
  \item Collaborated with QA teams for testing and vendor coordination.
\end{itemize}

\subsection*{Senior Firmware Engineer – 75F — Dec 2019 to Jan 2021}
\begin{itemize}[leftmargin=*]
  \item Built firmware for smart HVAC systems using Microchip SAMD/SAML with BLE and RF.
  \item Developed drivers for environmental sensors and managed BLE/RF stacks.
  \item Led debugging efforts and contributed to field issue resolution.
\end{itemize}

\subsection*{Embedded Design Engineer – Xpheno (Client: West Pharma) — Apr 2019 to Dec 2019}
\begin{itemize}[leftmargin=*]
  \item Developed BLE/NFC firmware on nRF52 for healthcare devices.
  \item Built BLE wake-up and low-power inductive load sensing features.
\end{itemize}

\subsection*{Advanced Consultant – Altran India (Client: Qualcomm, Intel) — Feb 2016 to Jan 2019}
\begin{itemize}[leftmargin=*]
  \item Led post-silicon validation and production test automation using Python and C.
  \item Validated SPI, QSPI, OSPI and SOC features across test environments.
\end{itemize}

\subsection*{Earlier Roles: POSH Labs, Real Time Signals, Nxt Gen Technologies (2013–2016)}
\begin{itemize}[leftmargin=*]
  \item Developed IoT prototypes using Contiki OS, CoAP, and ZigBee.
  \item Designed and tested embedded systems for home automation and vehicle tracking.
\end{itemize}

\section*{Education}
\textbf{M.Tech in Embedded Systems}, JNTU Anantapur — 2011–2013 \hfill (72\%) \\
\textbf{B.Tech in ECE}, JNTU Anantapur — 2007–2011 \hfill (60\%)

\end{document}
